---
title: Food Supply Datasets
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DT)
```

Below are the data tables used to create the visualizations in our article. The data below came from the [Food and Agriculture Organization of the United Nations](https://www.fao.org/home/en), and was seperated out, recombined, and cleaned by us, the data team. The specific dataset used was the [Suite of Food Security Indicators](https://www.fao.org/faostat/en/#data/FS), primarily the African and European continental regions (although some visualizations were created from global data in the early sections). Although not used in our analysis, a column was added concerning primary colonizing power, and African nations with a colonial history were thusly linked to their colonial power; the decisions used in determining colonial relationships can be found in the final data table.

## {.tabset}

### GDP

```{r gdp-table, echo=FALSE, warning=FALSE}
gdp <- read.csv("../data/CleanedData/gdp.csv", fileEncoding = "UTF-8")
datatable(gdp[,-1], options = list(searchHighlight = TRUE, pageLength = 5))
```

### Dietary Adequacy

```{r energy-table, echo=FALSE, warning=FALSE}
energy <- read.csv("../data/CleanedData/energyadequacy.csv", fileEncoding = "UTF-8")
datatable(energy[,-1], options = list(searchHighlight = TRUE, pageLength = 5))
```

### Food Stability by Gender

```{r gender-table, echo=FALSE, warning=FALSE}
gender <- read.csv("../data/CleanedData/foodinsecuritybygender_cleaned.csv", fileEncoding = "UTF-8")
datatable(gender[,-1], options = list(searchHighlight = TRUE, pageLength = 5))
```

### Obesity

```{r obesity-table, echo=FALSE, warning=FALSE}
obesity <- read.csv("../data/CleanedData/obesityadults.csv", fileEncoding = "UTF-8")
datatable(obesity[,-1], options = list(searchHighlight = TRUE, pageLength = 5))
```

### Malnutrition

```{r malnour-table, echo=FALSE, warning=FALSE}
malnour <- read.csv("../data/CleanedData/undernourishment.csv", fileEncoding = "UTF-8")
datatable(malnour[,-1], options = list(searchHighlight = TRUE, pageLength = 5))
```

### Political Stability

```{r politics-table, echo=FALSE, warning=FALSE}
politics <- read.csv("../data/CleanedData/politicalstability.csv", fileEncoding = "UTF-8")
datatable(politics[,-1], options = list(searchHighlight = TRUE, pageLength = 5))
```

### Protein Supply

```{r protein-table, echo=FALSE, warning=FALSE}
protein <- read.csv("../data/CleanedData/proteinsupply.csv", fileEncoding = "UTF-8")
datatable(protein[,-1], options = list(searchHighlight = TRUE, pageLength = 5))
```

### Colonial Relationship

```{r colonial-table, echo=FALSE, warning=FALSE}
colonial <- read.csv("../data/colonydata.csv", fileEncoding = "UTF-8")
datatable(colonial, options = list(searchHighlight = TRUE, pageLength = 5))
```
